Extended Data

### 2021-09-17 doc/manuscript/Dow_manuscript_Nature.Rmd
reduce n decimal points reported
@camerondow35 , FYI, one digit after the decimal point is sufficient here

For both ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the critical temperature window resulted in earlier achievement of growth milestones (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Consistent with findings from previous studies[@parmesan_globally_2003, @ibanez_forecasting_2010,@friedl_tale_2014], at our focal sites the DOYs of leaf greenup and mid-greenup (measured at ecosystem level via remote sensing) advanced with increasing $T_{max}$ during the critical temperature window (p=0.001 and 0.139, respectively). 
Specifically, greenup DOY advanced 4.535 days/$^\circ$C at SCBI and 2.437 days/ $^\circ$C at Harvard Forest when comparing the years with the warmest and coldest mean $T_{max}$ during the critical temperature window, and mid-greenup also advanced, but to a lesser extent (Fig. `r DOY_timing`).
Similarly, $DOY_{25}$ (SCBI: RP = -1.91 days/ $^\circ$C, DP = -3.47 days/$^\circ$C , HF: RP = -2.79 days/$^\circ$C, DP = -7.90 days/$^\circ$C ), $DOY_{50}$ (SCBI: RP = -1.54 days/ $^\circ$C, DP = -3.52 days/$^\circ$C, HF: RP =  -4.98 days/$^\circ$C, DP = -7.27 days/$^\circ$C), $DOY_{75}$ (SCBI: RP = -1.128 days/$^\circ$C, DP = -3.56 days/$^\circ$C , HF: RP = -7.17 days/$^\circ$C, DP= -6.62 days/$^\circ$C), and $DOY_{g.max}$ at both sites all decreased with mean $T_{max}$ during the critical temperature window during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`; see also Extended Data Figures `r EDF_pheno_Tmax_climwin`-`r EDF_pheno_Tmin_AprilMay`).

>>>>

For both ring- and diffuse- porous species at both sites, warmer $T_{max}$ in the critical temperature window resulted in earlier achievement of growth milestones (Figs. `r schematic_summary`, `r EDF_pheno_Tmax_climwin`).
Consistent with findings from previous studies[@parmesan_globally_2003, @ibanez_forecasting_2010,@friedl_tale_2014], at our focal sites the DOYs of leaf greenup and mid-greenup (measured at ecosystem level via remote sensing) advanced with increasing $T_{max}$ during the critical temperature window (p=0.001 and 0.139, respectively). 
Specifically, greenup DOY advanced 4.5 days/$^\circ$C at SCBI and 2.4 days/ $^\circ$C at Harvard Forest when comparing the years with the warmest and coldest mean $T_{max}$ during the critical temperature window, and mid-greenup also advanced, but to a lesser extent (Fig. `r DOY_timing`).
Similarly, $DOY_{25}$ (SCBI: RP = -1.9 days/ $^\circ$C, DP = -3.5 days/$^\circ$C , HF: RP = -2.8 days/$^\circ$C, DP = -7.9 days/$^\circ$C ), $DOY_{50}$ (SCBI: RP = -1.5 days/ $^\circ$C, DP = -3.5 days/$^\circ$C, HF: RP =  -5.0 days/$^\circ$C, DP = -7.3 days/$^\circ$C), $DOY_{75}$ (SCBI: RP = -1.1 days/$^\circ$C, DP = -3.6 days/$^\circ$C , HF: RP = -7.2 days/$^\circ$C, DP= -6.6 days/$^\circ$C), and $DOY_{g.max}$ at both sites all decreased with mean $T_{max}$ during the critical temperature window during the critical temperature window (Figs. `r schematic_summary`, `r DOY_timing`; see also Extended Data Figures `r EDF_pheno_Tmax_climwin`-`r EDF_pheno_Tmin_AprilMay`).
